### 2013-11-03 proposal/proposal/chapter1.tex
changes

\setcounter{chapter}{0}
%*******************************START INTRODUCTION **********************************
\chapter{Introduction}\label{sec:intro}
In this chapter we introduce the context of this research, which is about argumentation-based negotiation dialogue games. We also present the motivations behind this work and the research questions. Also, we discuss the objective of this research and our preliminary contributions. Proposal organization is presented in the last section.

@@

Autonomous agents and multiagent systems (MAS) provide a technology offering an alternative for the design of intelligent and cooperative
systems. Recently, efforts have been made to develop novel tools, methods, and frameworks to establish the necessary standards for wider
use of MAS as an emerging paradigm ~\cite{Mehdi03}. An increasing interest within this paradigm is on modeling interactions and dialogue systems.
In fact, several dialogue systems have been proposed in the literature for modeling \emph{information seeking} dialogues (e.g.,~\cite{MWParsons03}),
\emph{inquiry} dialogues (e.g.,~\cite{BlackH07,Black09}), \emph{deliberation} dialogues (e.g.,~\cite{Tolchinsky2012}), \emph{persuasion}
dialogues (e.g., ~\cite{Amgoud00}), and \emph{negotiation} dialogues (e.g., ~\cite{KSycara90}), which are our concern in this paper.
Negotiation is a form of interaction in which a group of agents, with conflicting interests, but a desire to cooperate, try to come to a mutually
acceptable agreement on the division of scarce resources~\cite{Rahwan03,Bentahar07}. It is worth noting that in all types of dialogue systems
mentioned above, a dialogue game is a normative model of dialogue, which mainly consists of: i) a set of moves (e.g., challenge, assertion, question, etc.);
ii) one commitment store for each conversant where the advanced moves are stored; iii) a communication language specifying the locution that will be
used by agents during a dialogue for exchanging moves; iv) a protocol specifying the set of rules governing the dialogues; and v) agents' strategies,
which are the different tactics used by agents for selecting their moves at each step in the dialogue~\cite{AmgoudS08}. A dialogue correctly proceeds
as long as the participants conform to the dialogue rules and eventually ends when some termination rules are achieved~\cite{AmgoudS08,Nicolas03,Prakken01}.

In the recent years, argumentation theory has been widely investigated and used to model and analyze dialogue games~\cite{BentaharAIR,BentaharKBS10,Reed06,Mahalakshmi09}.
Argumentation provides a powerful tool to represent, model, and reason about dialogue moves, strategies, and dialogue outcomes. The core idea is the ability
to support moves with justifications and explanations, which play a key role in persuasion and negotiation settings~\cite{GarciaCRS13}. In this paper, we
will focus on the exchanged moves in a dialogue game (i.e., the dialogue itself) and the agents playing these moves when supporting arguments are used.
The main issue we are investigating is the uncertainty index of selecting the right moves during the dialogue, the certainty index that the selected move
will be accepted by the addressee, and the uncertainty index of the whole dialogue. Uncertainty can be thought of as being the inverse of information. Information
about a particular engineering or scientific problem may be incomplete, imprecise, fragmentary, unreliable, vague, contradictory, or even deficient~\cite{RossJA13}.
Uncertainty about values of given variables (e.g., the disease affecting a patient in medical applications) can result from some errors and hence from unreliability
(in the case of sensors) or from different background knowledge (in the case of agents). As a result, it is possible to obtain different uncertain pieces of
information about a given value from different sources~\cite{Jenhani07}. Our aim is to investigate the uncertainty issues that the agent faces when choosing an
argument to play in argumentation-based negotiations. In the literature, many efforts have been deployed to model negotiation. A brief description of those efforts
is given in the following subsection.

A multiagent system is a system where agents (software autonomous entities) are allowed to freely enter and leave the
system, thus making the environment continuously changing. These agents need to communicate with each other, with individual or
collective tasks, with different resources, and different skills. As a result, these agent societies are becoming more and more
similar to the human ones~\cite{Falcone99}.\\
An attractive characteristic of MAS is that agents can act more effectively in groups. Agents are designed to
autonomously collaborate with each other in order to satisfy both their internal goals and the shared external demands
generated by virtue of their participation in agent societies. \\
The languages used by agents to communicate are called Agent Communication Languages (ACLs). The main objective of an
ACL is to model a suitable framework that allows heterogeneous agents to interact and to communicate with meaningful
statements that convey information about their environment or knowledge~\cite{Kone00}. Two main ACLs have been proposed:
the Knowledge Query and Manipulation Language (KQML)~\cite{Finin95}, and the Foundation for Intelligent Physical Agents'
Agent Communication Language (FIPA-ACL)~\cite{Fipa01}.\\
Furthermore, there is an increasing interest on modeling interactions and dialogue systems. Indeed, several
dialogue systems have been proposed in the literature for modeling information seeking dialogues (e.g.~\cite{MWParsons03}),
inquiry dialogues (e.g.,~\cite{BlackH07}), persuasion dialogues (e.g.,~\cite{Amgoud00}) and finally negotiation dialogues
(e.g.,~\cite{KSycara90}).\\
Evaluating multiagent systems and the dialogues taking place between the participants is a very important issue in the recent
developments of multiagent systems. The existing approaches on evaluating these systems are focusing on one aspect at a time, such as
evaluating persuasion dialogues (~\cite{Amgoud00}), and measuring the impact of argumentation (~\cite{Hunter04}). They are more concerned
with proposing dialogue strategies and analyzing dialogues. However, nothing is said about the agents' certainty about their dialogues and
the goodness degree of the agents in the dialogues. In this thesis, we are interested particularly in negotiation dialogue games. In fact,
negotiation is a form of interaction in which a group of agents, with conflicting interests, but a desire to cooperate, try to come to a
mutually acceptable agreement on the division of scarce resources ~\cite{Rahwan03,Bentahar07}. Dialogue games are a set of rules governing the
dialogue. such rules specify the allowed communicative acts agents can perform when participating in  a dialogue. Precisely, we focus in this
work on quantitative negotiation dialogue games such as bargaining. We will focus first on the exchanged moves (i.e. the dialogue itself) in
terms of the certainty index of selecting the right moves during the dialogue, and the certainty index of the whole dialogue. Uncertainty about
values of given variables (e.g. the disease affecting a patient in medical applications) can result from some errors and hence from non-reliability
(in the case of sensors) or from different background knowledge (in the case of agents). As a result, it is possible to obtain different uncertain
pieces of information about a given value from different sources ~\cite{Jenhani07}. The second focus of this thesis is on the agents' strategies in
terms of goodness degree of the agents in the real dialogue (i.e. the dialogue that effectively happened between the participants) and the farness
degree of the agents from the right dialogue (i.e. the best dialogue that can be produced by two agents if they know the knowledge bases of each other).
For example in negotiation setting, the best dialogue is the one in which with a minimum number of moves, two agents can achieve the best agreement for
both of them, if such an agreement exists considering the knowledge bases of these two agents.
%

@@

Multiagent systems are widely used in everyday life, and to add more value to these systems in the field of software engineering,
they supposed to be measurable. Our motivation is to find a way to measure these systems from different aspects such as measuring
the dialogues, the performance of the participants in the dialogues, and the protocols governing the dialogues, etc. In order to evaluate
dialogues in multiagent systems, we define a new set of measurements from an external agent's point of view. Defining measures for the
participants in the dialogues is another motivation in this thesis. The aim behind developing such measurements is to help engineers and
developers of agent-based systems in evaluating these systems and their performances.\\

\indent When monitoring a dialogue between two or more agents, there are many question that should be answered. In this thesis, we are interested in answering the following questions:

\begin{itemize}
\item How much are agents certain about selecting a move at each dialogue step?
\item How much are agents certain about their dialogues?
\item How good are agents in the real dialogue (i.e. the effective dialogue)?
\item How far are agents from the right dialogue (i.e. the best dialogue given the knowledge bases of the participants)?
\end{itemize}
Answering these questions is undoubtedly complex. Therefore, we do not expect a comprehensive answer to all these questions.

@@

The main objective of this thesis is to develop a new set of measurements for negotiation dialogue games to help in evaluating and
comparing different negotiation dialogues with different participants for the same topic. The importance of introducing measures for
negotiation dialogue games at each step of the dialogue such as measuring how much the agent is certain about its move is to help in developing intelligent multiagent systems (MAS) and to help evaluating different agents provided by different developers.\\
\indent Our research aims to ensure that the agents' certainty about their dialogue is fairly represented at each step during
the dialogue by making sure that the agent's certainty about selecting the right move is kept in mind and considered as a property
of multiagent systems.\\
\indent The main contribution of this thesis is the proposition of a new set of measures for dialogue games from an external agent's point of view.
In particular, we introduce two sets of measurements. In the first set  we use Shannon entropy to measure the certainty index of the dialogue.
This involves i) using Shannon entropy to measure the agent's certainty about each move during the dialogue; and ii) using
Shannon entropy to measure the certainty of the agents about the whole dialogue with two different ways. The first way is
by taking the average of the certainty index of all moves, and the second way is by determining all possible dialogues and
applying the general formula of Shannon entropy. In the second set, we are measuring how good are agents in the real dialogue
\emph{(Goodness Degree )}, and measuring how far are agents from the right dialogue \emph{(Farness Degree)}~\cite{Marey09}.

As mentioned earlier, there exist several proposals on the argumentation-based negotiation. Most of them are concerned with proposing protocols to show how agents can
interact with each other, and how arguments and offers can be generated, evaluated and exchanged during the negotiation process. However, none of them has investigated
the agents' uncertainty about the exchanged arguments and how such an uncertainty could be measured at each dialogue step to assist the agents make a better decision. The
uncertainty is generally defined as ``that which is not precisely known''. This definition permits the identification of different kinds of uncertainty arising from different
sources and activities, most of which go unnoticed in analysis. To the best of our knowledge, this work is the first of it's kind in dealing with the agent's uncertainty
while making a decision at each dialogue step in order to achieve an agreement. In this paper, we define a new set of uncertainty measures for dialogue games from an
external agent's point of view. In particular, we distinguish two types of uncertainty: \textbf{Type I} and \textbf{Type II}.

Type I is about the uncertainty of playing the right move (i.e., advancing the right argument) at each dialogue step. For this type, we use Shannon entropy to measure: i) the
uncertainty index of the agent that he is selecting the right move at each step during the dialogue; and ii) the uncertainty index of both agents participating in the dialogue
about the whole dialogue. The latter measurement will be conducted in two different ways. The first way is by taking the average of the uncertainty index of all moves,
and the second is by determining all possible dialogues based on the union of the agents' knowledge bases and applying the general formula of Shannon entropy.

Type II is about the uncertainty of the agent that the selected move (argument) will be accepted by the addressee (from now on we will call this second type of uncertainty
by \emph{uncertainty degree}). In this context, we introduce a new classification of arguments based on their certainty index. These measures are of great importance since
they can be used as guidelines for a protocol in order to generate the best dialogue between autonomous intelligent agents.

Figure \ref{fig1.0} summarizes the whole proposed approach where the certainty index ($CI$) and weighted certainty index ($W\_CI$) of the moves and the whole dialogue are
measured for Type I. For Type II, different cases are considered depending on how many arguments are in use.

\begin{figure}[t]
                \begin{center}
                \includegraphics[width=15cm, height=11cm]{Figures/Approach1.eps}
                \end{center}
                \caption{General overview of the approach}\label{fig1.0}
                \label{Stack}
                \end{figure}

\section{Research outline}\label{sec:outline}
The rest of the paper is organized as follows: In Section~\ref{sec:Argumentation}, we present a  brief theoretical background on the argumentation system
and agent's theory, strategic reasoning, tactic reasoning and risk of failure notions are also discussed in this section. In Section~\ref{sec:uncertainty},
we present the agent's uncertainty measures using Shannon entropy, which include type I (measuring the uncertainty of the agent about selecting the right move)
and type II (measuring the uncertainty degree that the selected move will be accepted). Argument classification is also presented in this section. Related work
is discussed in Section~\ref{sec:related}. Finally, conclusion and future work are presented in Section~\ref{sec:conclusion}.

>>>>

\setcounter{chapter}{0}
%*******************************START INTRODUCTION **********************************
\chapter{Introduction}\label{sec:intro}
In this chapter we introduce the context of this research, which is about community of web services as autonomous agents and cooperative game theoretic solution concepts. We discuss literature review and their shortcomings then present the motivations behind this work. Also, we discuss our preliminary contributions.

@@

@@

Over the past years, online services have become part of many
scalable business applications. The increasing reliance on
web-based applications has significantly influenced the way web
services are engineered. Web services provide a set of stateless
software functions accessible at a network address over the web.
The recent developments are shifting web services from passive and
individual components to autonomous and group-based components
where interaction, composition, and cooperation are the key
challenges \cite{ICWS2011-1,SCC2011-1}. The main objective is to
achieve a seamless integration of business processes, applications
and web services. Delivering high quality services considering the
dynamic and unpredictable nature of the Internet is still a very
critical and challenging issue.

The need for highly available and responsive services has called
for grouping and collaborative mechanisms of loosely-coupled web
services, particularly in business settings. The idea of grouping
web services within communities and the way those communities are
engineered so that web services can better collaborate have been
proposed and investigated in
\cite{DBLP:journals/ijebr/MaamarSTBB09,DBLP:journals/internet/BenatallahSD03,Rosario:2008:PQS:1512146.1512290}.
Communities are virtual groups of web services having similar
functionalities \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038,Medjahed05adynamic,10.1109/ARES.2008.7}, but probably different non-functional quality
attributes, which form the QoS parameters. When communities are
used, users send their requests to the masters of those
communities, which are responsible of managing the communities,
forwarding the requests to the suitable member web services and
checking the credentials of those members. Communities aim to
provide higher service availability and performance than what
individual web services can provide. The high availability of
services and the community resilience to failure are guaranteed
since web services can cooperate and replace each other within the
same community and since there is no single point of failure in
the communities architecture.

Most of the recent work on communities of services are either
user-centric and focus on user satisfaction
\cite{Chun02user-centricperformance} or system-centric and focus
on the whole system throughput, performance and utilization. There
are many contributions in distributed, grid, cluster and cloud
services which are system-centric. However, in real world
environments and applications, both users and service providers
are self-interested agents, aiming to maximize their own profit.
In those environments, both parties (users and services) will
collaborate as long as they are getting more benefits and payoff.

In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
users and services to maximize their gain. A two-player
non-cooperative game between web services and community master was
introduced in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this
game-theoretic model, the strategies available to a web service
when facing a new community are requesting to join the community,
accepting the master's invitation to join the community, or
refusing the invitation to join. The set of strategies for
communities are inviting the web service or refusing the web
service's join request. Based on their capacity, market share and
reputation, the two players have different set of utilities over
the strategy profiles of the game. The main limits of this game
model are: 1) its consideration of only three quality parameters,
while the other factors are simply ignored; and 2) the
non-consideration of the web services already residing within the
community. The game is only between the community master and the
new web service, and the inputs from all the other members are
simply ignored. The consideration of those inputs is a significant
issue as existing web services can lose utility or payoff because
of the new member, which can results in an unhealthy and unstable
group. The problem comes from the fact that the existing members
should collaborate with the new web services, so probably their
performance as a group can suffer. Existing members may even
deviate and try to join other communities if they are unsatisfied.
Those considerations of forming stable and efficient coalitions
are the main contributions of our paper.

In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
for selecting web services has been proposed. In this approach,
the authors proposed a web service selection process that the
community masters can use. The approach considers the efficiency
of all the three involved parties, namely users, web services and
communities. In this work, it is shown how the gains of these
parties are coupled together using a linear optimization process.
However, the optimization problem in this solution tends to
optimize some parameters considering all web services regardless
of their efficiency and contribution to the community's welfare.
Moreover, there are no clear thresholds for accepting or rejecting
new web services. The solution of the optimization problem could,
for instance, suggest web services already residing within the
community to increase or decrease their capacity to cover up the
weakness of other parties in the system. However, a high
performing web service could deviate anytime it finds itself
unsatisfied within the community instead of adjusting its service
parameters.

In \cite{10.1109/TSC.2012.12}, a cooperative scheme among autonomous
web services based on coalitional game theory has been introduced. They have proposed an algorithm to
reach individually stable coalition partition for web services in order to
maximize their efficiency. The communities choose new web services on the promise
that it would benefit the community without decreasing any other web service's
income. In their model, the worth of community is evaluated with high emphasis on
availability metric and considering price and cost values only. The community structure is based on a coordination chain,
where a web service is assigned as a \emph{primary} web service and the community task destribution
method, will initially invoke the primary web service and only if the primary web service is unavailable
will invoke the next backup web services as they are ordered in the coordination chain. However in cooperative models, it is preferred to
have a real and active cooperative activity engaging all agents to perform the tasks more efficiently. Especially nowadays
with recent advancement in cloud and hardware infrastructures availability is becoming less of an issue. So the backup web services
in their model have a very low chance of getting jobs, especially the ones further in chain, which is huge waste of web services
capabilities.

% ooooooold
%\indent When monitoring a dialogue between two or more agents, there are many question that should be answered. In this thesis, we are interested in answering the following questions:
%\begin{itemize}
%\item How much are agents certain about selecting a move at each dialogue step?
%\item How much are agents certain about their dialogues?
%\item How good are agents in the real dialogue (i.e. the effective dialogue)?
%\item How far are agents from the right dialogue (i.e. the best dialogue given the knowledge bases of the participants)?
%\end{itemize}
%Answering these questions is undoubtedly complex. Therefore, we do not expect a comprehensive answer to all these questions.

@@

In this research work, we use game theory to
propose a cooperative game model for the aggregation of web
services within communities. The solution concepts of our
cooperative game seeks to find efficient ways of forming
coalitions (teams) of web services so that they can maximize their
gain and payoff, and distribute the gain in a fair way among all
the web services. Achieving Fairness when the gain is distributed
among the community members is the main factor to keep the
coalition stable as no web service will expect to gain better by
deviating for the community. In other words, the coalition is made
efficient if all the members are satisfied. We first propose a
representation function for communities of web services based on
their QoS attributes. By using this function, we can evaluate the
$worth$ of each community of web services. When facing new
membership requests, a typical community master checks whether the
new coalition having the old and new set of web services will keep
the community stable or not. The community master will reject the
membership requests if it finds out that the new coalition would
be unstable, preventing $any$ subset of web services from gaining
significantly more by deviating from the community and joining
other communities or forming new ones. The computation of
solutions for cooperative game theory problems is combinatorial in
nature and proven to be NP-complete \cite{Algorithmic}, making
this computation impractical in real world applications. However,
using the concepts of coalition stability, we propose
approximation algorithms running in polynomial time providing web
services and community masters with applicable and near-optimal
decision making mechanisms.

\section{Research outline}\label{sec:outline}
The rest of the paper is organized as follows: In Section~\ref{sec:Argumentation}
